Issues with Dynamical Measurements Across the Disk

### 2019-02-26 paper/ms.tex
Fix colors

From Figure \ref{fig:range_deltaphi} it is clear that the range of midplane
values spanned in a given $\Delta \phi$ quickly saturates at $\Delta \phi
\gtrsim \pi/2$ radians (i.e. one quarter of the way around the Galactic disk
from the Sun). At far smaller $\Delta \phi$ it reaches the level of deviation
required for an $\mathcal{O}(1)$ systematic error in $J_z$ for our fiducial
thin-disk-like orbit (*color1* horizontal line in Figure
\ref{fig:range_deltaphi}). For the three simulations considered, the median
range exceeds this value at $\Delta \phi >$ XX, YY, and ZZ radians, with
corresponding physical scales of $\lambda \sim$ XX, YY, and ZZ parsecs. These
can be considered estimates of the range of validity for an extension of the
locally determined axisymmetric coordinate system, at least when it comes to
the study of stars on quasi-circular orbits.

The situation is more forgiving for the study of thick-disk-like orbits, where
an $\mathcal{O}(1)$ systematic error in $J_z$ requires a larger midplane
deviation (*color2* horizontal line in Figure \ref{fig:range_deltaphi})
corresponding to $\Delta \phi >$ XX, YY, and ZZ radians or $\lambda \sim$ XX,
YY, and ZZ parsecs. For stars on halo-like orbits, extending the local
coordinate system globally is not likely to cause serious problems, since the
midplane deviations are relatively small compared to those needed to produce
$\mathcal{O}(1)$ systematic errors in the actions (*color3* horizontal line in
Figure \ref{fig:range_deltaphi}). However, we caution that the tendency of
these midplane deviations is to \emph{inflate} the value of $J_z$ for thin
disk stars in an extremely non-Gaussian way (Figure \ref{fig:Jz_hist}),
scattering them into the region of action space normally associated with
different stellar populations and possibly contributing to confusion there.

>>>>

From Figure \ref{fig:range_deltaphi} it is clear that the range of midplane
values spanned in a given $\Delta \phi$ quickly saturates at $\Delta \phi
\gtrsim \pi/2$ radians (i.e. one quarter of the way around the Galactic disk
from the Sun). At far smaller $\Delta \phi$ it reaches the level of deviation
required for an $\mathcal{O}(1)$ systematic error in $J_z$ for our fiducial
thin-disk-like orbit (\thincolor horizontal line in Figure
\ref{fig:range_deltaphi}). For the three simulations considered, the median
range exceeds this value at $\Delta \phi >$ XX, YY, and ZZ radians, with
corresponding physical scales of $\lambda \sim$ XX, YY, and ZZ parsecs. These
can be considered estimates of the range of validity for an extension of the
locally determined axisymmetric coordinate system, at least when it comes to
the study of stars on quasi-circular orbits.

The situation is more forgiving for the study of thick-disk-like orbits, where
an $\mathcal{O}(1)$ systematic error in $J_z$ requires a larger midplane
deviation (\thickcolor horizontal line in Figure \ref{fig:range_deltaphi})
corresponding to $\Delta \phi >$ XX, YY, and ZZ radians or $\lambda \sim$ XX,
YY, and ZZ parsecs. For stars on halo-like orbits, extending the local
coordinate system globally is not likely to cause serious problems, since the
midplane deviations are relatively small compared to those needed to produce
$\mathcal{O}(1)$ systematic errors in the actions (\halocolor horizontal line
in Figure \ref{fig:range_deltaphi}). However, we caution that the tendency of
these midplane deviations is to \emph{inflate} the value of $J_z$ for thin
disk stars in an extremely non-Gaussian way (Figure \ref{fig:Jz_hist}),
scattering them into the region of action space normally associated with
different stellar populations and possibly contributing to confusion there.
